\LARGE \bf Child-Robot Spatial Arrangement in a Learning by Teaching Activity

### 2016-05-27 paper-Ro_Man-2016.tex
changes from reviewers requests

\usepackage[pdftex]{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\graphicspath{}
%\usepackage[utf8]{inputenc}
\usepackage{slashbox}
\setlength{\belowcaptionskip}{-8pt}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

@@

\author{Wafa Johal$^{1}$$^{2}$, Alexis Jacq$^{1}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
\thanks{}% <-this % stops a space
\thanks{$^{1}$ CHILI Lab,
	$^{2}$ LSRO Lab,
        \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Switzerland
        {\tt\small firstname.lastname@epfl.ch}}%
\thanks{$^{3}$Instituto Superior T\'{e}cnico (IST), University of Lisbon, Portugal
        {\tt\small firstname.lastname@inesc-id.pt}}%
}

@@

\begin{figure*}
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.7\linewidth]{./figures/f2f_photot.png}
  \caption{Face to face spatial formation}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.7\linewidth]{./figures/s2s_photo2t.jpg}
  \caption{Side by Side spatial formation}
  \label{fig:sub2}
\end{subfigure}
 \caption{Experimental set-ups showing the \emph{with-me-ness} targets in the rectangles: orange - the writing tablet,  blue - the robot's head, green - the tablet used to select a word to teach to the robot}
\label{fig:test}
\end{figure*}

@@

For this experiment, the targets were: "the observer"(a teacher or a teacher assistant),"the experimenter",  "the selection tablet"(the tablet used to pick a word) and the "tablet".
The with-me-ness is initially set to 0.5 and takes values from 0 to 1.
According to the state in which the activity is, (robot is writing, child is writing,\dots) the with-me-ness will be increased if the child looks at a target that is in the set of task-related targets (expected within this particular state of the activity).
We record these targets and the with-me-ness at a frequency of about $1Hz$.
The evolution of the withmeness is computationally attenuated in order to remove noisy data (by using the weighted cumulative of the withmeness value).

@@

Again, we observed an order effect with the withmeness increasing between the two sessions. 
As children were more confordable with the system, it is logic that they started to learn the dynamics of the interaction knowing when to look at the selection tablet, the writing tablet and the robot. 
%todo add stats
%	session	N	new_w	sd	se	ci
%	1	1	8886	0.7248584	0.2175269	0.002307596	0.004523421
%	2	2	7103	0.7965673	0.1691839	0.002007419	0.003935140
%Error: Within
%Df Sum Sq Mean Sq F value Pr(>F)    
%session       1   12.8  12.797   339.8 <2e-16 ***
%Residuals 15985  602.0   0.038

\subsection{Performances}
%\begin{figure}
%\centering
%\includegraphics[width=0.4\linewidth]{figures/plots/score_alone_se}
%\caption{Learning speed According to group or alone modality}
%\label{fig:score_alone_ci}
%\end{figure}
\subsubsection{Response Time and Writing Time}
Figure \ref{fig:times} shows on the left the average number of demonstration for each word taught to the robot for the two spatial arrangement conditions. 
There was no significant difference between the conditions even-though the average number of demonstration given by the child in the side-by-side condition seems higher than the face-to-face.

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.25\linewidth]{figures/plots/repetition_fformation_ci}
	\includegraphics[width=0.25\linewidth]{figures/plots/responseTime_fformation_ci}
	\includegraphics[width=0.25\linewidth]{figures/plots/writingTime_fformation_ci2}
	\caption{Number of demonstration per word (left), response time (center), writing time (right) - (Means and Confidence Intervals)}
	\label{fig:times}
	\end{figure*}

These results show that children when not spending more time per word in one condition of the other. 
The spatial condition didn't influence the involvement of the child in the task. 
% The effect of the group variable on the score of the child was statistically significant ( $F_{1,279}= 6.928, p<0.01$). The score was greater($M=0.41, SD=0.11, N=141$) in  the alone condition compare to the group condition ($M= 0.37, SD=0.11, N=140$).
%These results confirm the fact that the robot is better suited here for individual interaction. 
\subsubsection{Writing Score for the Robot}
There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Repeated measures within subjects:$p>0.1$).
This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
However, results showed significant differences in terms of feedback given to the robot regarding the score of the robot.

@@

Table~\ref{proba} shows the probabilities of transition from after the score increases and after the score decreases.
We notice that in general the positive feedback probabilities are higher for the side-by-side condition in comparison to the face-to-face. 
On the contrary, the probability of having a negative feedback after is higher in the face-to-face condition.
We can also notice that when the score decreases, the probability of having a positive feedback is almost twice higher in the side-by-side condition (total number of events $= $).

@@

@@

To conclude, we believe that spatial arrangement can be used as a non-verbal cue of communication to contextualize the interaction (as cooperative or competitive for instance).
%discuss results regarding the literature, same ? different arguments for/against initial premise, limitations, etc.

@@

\small
\bibliographystyle{abbrv}
\bibliography{fformation_cowriter}

>>>>

\usepackage[pdftex]{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\graphicspath{}
%\usepackage[utf8]{inputenc}
\usepackage{slashbox}
\setlength{\belowcaptionskip}{-11pt}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

@@

\author{Wafa Johal$^{1,}$$^{2}$, Alexis Jacq$^{1,}$$^{3}$, Ana Paiva$^{3}$ and Pierre Dillenbourg$^{1}$  % <-this % stops a space
\thanks{}% <-this % stops a space
\thanks{$^{1}$ CHILI Lab,
	$^{2}$ LSRO Lab,
        \'{E}cole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Switzerland
        {\tt\small firstname.lastname@epfl.ch}}%
\thanks{$^{3}$Instituto Superior T\'{e}cnico (IST), University of Lisbon, Portugal
        {\tt\small firstname.lastname@inesc-id.pt}}%
}

@@

\begin{figure*}
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.7\linewidth]{./figures/f2f_photott.jpg}
  \caption{Face to face spatial formation}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.7\linewidth]{./figures/s2s_photo2t.jpg}
  \caption{Side by Side spatial formation}
  \label{fig:sub2}
\end{subfigure}
 \caption{Experimental set-ups showing the \emph{with-me-ness} targets in the rectangles: orange - the writing tablet,  blue - the robot's head, green - the tablet used to select a word to teach to the robot}
\label{fig:test}
\end{figure*}

@@

For this experiment, the targets were: "the observer"(a teacher or a teacher assistant),"the experimenter",  "the selection tablet"(the tablet used to pick a word) and the "tablet".
The with-me-ness is initially set to 0.5 and takes values from 0 to 1.
According to the state in which the activity is, (robot is writing, child is writing,\dots) the with-me-ness will be increased if the child looks at a target that is in the set of task-related targets (expected within this particular state of the activity).
We record these targets and the with-me-ness at a frequency of about $1Hz$.
The evolution of the with-me-ness is computationally attenuated in order to remove noisy data (by using the weighted cumulative of the with-me-ness value).

@@

Again, we observed an order effect with the with-me-ness increasing between the two sessions. 
As children were more comfortable with the system, it is logic that they started to learn the dynamics of the interaction knowing when to look at the selection tablet, the writing tablet and the robot. 
%todo add stats
%	session	N	new_w	sd	se	ci
%	1	1	8886	0.7248584	0.2175269	0.002307596	0.004523421
%	2	2	7103	0.7965673	0.1691839	0.002007419	0.003935140
%Error: Within
%Df Sum Sq Mean Sq F value Pr(>F)    
%session       1   12.8  12.797   339.8 <2e-16 ***
%Residuals 15985  602.0   0.038        
\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.25\linewidth]{figures/plots/repetition_fformation_ci}
	\includegraphics[width=0.25\linewidth]{figures/plots/responseTime_fformation_ci}
	\includegraphics[width=0.25\linewidth]{figures/plots/writingTime_fformation_ci2}
	\caption{Number of demonstration per word (left), response time (center), writing time (right) - (Means and Confidence Intervals)}
	\label{fig:times}
\end{figure*}
\subsection{Performances}
%\begin{figure}
%\centering
%\includegraphics[width=0.4\linewidth]{figures/plots/score_alone_se}
%\caption{Learning speed According to group or alone modality}
%\label{fig:score_alone_ci}
%\end{figure}
\subsubsection{Response Time and Writing Time}
Figure \ref{fig:times} shows on the left the average number of demonstration for each word taught to the robot for the two spatial arrangement conditions. 
There was no significant difference between the conditions even-though the average number of demonstration given by the child in the side-by-side condition seems higher than the face-to-face.

@@

These results show that children when not spending more time per word in one condition of the other. 
The spatial condition didn't influence the involvement of the child in the task. 
% The effect of the group variable on the score of the child was statistically significant ( $F_{1,279}= 6.928, p<0.01$). The score was greater($M=0.41, SD=0.11, N=141$) in  the alone condition compare to the group condition ($M= 0.37, SD=0.11, N=140$).
%These results confirm the fact that the robot is better suited here for individual interaction.

\subsubsection{Writing Score for the Robot}
There was no significant difference of writing score in the F-formation condition tested (side-by-side:$M=0.80, SD=0.08, N=135$, face-to-face: $M=0.79, SD=0.08, N=191$, Anova Repeated measures within subjects:$p>0.1$).
This result means that the children were teaching as well in the face-to-face condition as in the side-by-side condition.
However, results showed significant differences in terms of feedback given to the robot regarding the score of the robot.

@@

@@

Table~\ref{proba} shows the probabilities of transition of feedback events (positive or negative) after the score increases or after the score decreases (computed using Markov Chain).
We notice that in general the positive feedback probabilities are higher for the side-by-side condition in comparison to the face-to-face. 
On the contrary, the probability of having a negative feedback after is higher in the face-to-face condition.
We can also notice that when the score decreases, the probability of having a positive feedback is almost twice higher in the side-by-side condition (total number of events $= $).

@@

To conclude, we believe that spatial arrangement can be used as a non-verbal cue of communication to contextualize the interaction (as cooperative or competitive for instance). We also believe that choices in terms of spatial arrangements in HRI studies should be thoroughly made as they may influence the interaction. 
%discuss results regarding the literature, same ? different arguments for/against initial premise, limitations, etc.

@@

\small
\bibliographystyle{ieeetr}
\bibliography{fformation_cowriter}
